\LARGE \bf Matrix Multiplication-Driven Repulsive Fields for 3D Voxel-Based TSDF Calculation

### 2024-03-15 Articles/IROS/root.tex
rewritten introduction

@@

@@

The robots environment is modelled by discrete voxels. As the robots environment can dynamically change, we propose a method that looks at the surrounding space of the robot and calculates these direction away from all the surrounding obstacles in real time. We only look in a predefined area / perimeter arround the robot.

In 3D computer graphics, a voxel represents a value on a regular grid in three-dimensional space. Each of the voxels holds the probability value of its occupation. In case of voxel being empty it holds the value of 0, if the voxel is occupied it holds the value of non-zero, depending on our assurance of it being occupied. If it is definitly occupied it holds the value of 1.

In our method, we compute repulsive velocities within the task space using a novel matrix kernel multiplication approach. Concentrating on the task space is advantageous as it provides a more direct and realistic representation of the environment.

\replace{Naša metoda je posebno primerna za uporabo z senzorskimi sistemi kot so LIDAR ali globinske kamere, saj zaradi upoštevanja celotne okolice točke in ne le razdalje do najbližje točke v okolici efektivno filtriramo senzorski šum.}{prestavi to v diskusijo}

>>>>

%The robots environment is modelled by discrete voxels. As the robots environment can dynamically change, we propose a method that looks at the surrounding space of the robot and calculates these direction away from all the surrounding obstacles in real time. We only look in a predefined area / perimeter arround the robot.  
%
%In 3D computer graphics, a voxel represents a value on a regular grid in three-dimensional space. Each of the voxels holds the probability value of its occupation. In case of voxel being empty it holds the value of 0, if the voxel is occupied it holds the value of non-zero, depending on our assurance of it being occupied. If it is definitly occupied it holds the value of 1.

Robots need to quickly adapt to changes in dynamic environment, especially when obstacles appear. Our method helps a robot calculate safe directions away from obstacles by looking at the space around it in real-time. The focus is on a set area around the robot.

In 3D graphics, a voxel is like a tiny cube in a grid that makes up the space. We use voxels to map the workspace of the robot, each voxel has a value that tells us if it’s probably empty or occupied. A zero means empty, and a one means definitely something is there, with values in between showing varying levels of certainty.

The grid of voxels can be set in advance to match the layout of the space. We can also change the values in the voxels if we know where other objects or agents are moving. Besides pre-setting, we can use sensors to detect what's around.

Our method calculates repulsive velocities, which are vectors that guide the robot on where not to go by pointing away from potential collisions. These vectors gain strength as the robot approaches an obstacle, signaling an urgent need to maneuver to safety. Conversely, when the robot is positioned at an equal distance from obstacles in the vicinity—safely away from all potential collisions—the repulsive velocities weaken because there’s no immediate need to move.

%In our method, we compute repulsive velocities within the task space using a novel matrix kernel multiplication approach. Concentrating on the task space is advantageous as it provides a more direct and realistic representation of the environment.

%\replace{Naša metoda je posebno primerna za uporabo z senzorskimi sistemi kot so LIDAR ali globinske kamere, saj zaradi upoštevanja celotne okolice točke in ne le razdalje do najbližje točke v okolici efektivno filtriramo senzorski šum.}{prestavi to v diskusijo}

@@

\add{ADD}

@@
